Pillar 1 - Sequential Pattern Mining

### 2019-01-30 Pillar 1 - Sequential Pattern Mining.Rmd
SR save change

SR_expanded   <- my_SR(data = sequences_expanded   )
SR_expanded_PF <- my_SR(data = sequences_expanded_PF)
SR_expanded_HL <- my_SR(data = sequences_expanded_HL)
#Saving sequence rules
SR <- list(
    SR = SR,
    SR_PF = SR_PF,
    SR_HL = SR_HL,

    SR_expanded    = SR_expanded,
    SR_expanded_PF = SR_expanded_PF,
    SR_expanded_HL = SR_expanded_HL
    )

save(SR, file = "App/SR.RDATA")

>>>>

SR_expanded   <- my_SR(data = sequences_expanded   )
SR_expanded_PF <- my_SR(data = sequences_expanded_PF)
SR_expanded_HL <- my_SR(data = sequences_expanded_HL)
#Saving sequence rules
save(
    SR = SR,
    SR_PF = SR_PF,
    SR_HL = SR_HL,

    SR_expanded    = SR_expanded,
    SR_expanded_PF = SR_expanded_PF,
    SR_expanded_HL = SR_expanded_HL,

    file = "App/SR.RDATA")
